Claret: Using Data Types for Highly Concurrent Distributed Transactions

### 2015-02-14 rmd/paper.Rmd
more space hacks

```{r followers, fig.cap="CDF of the number of followers for users generated by the Kronecker synthetic graph generator, matching the power-law degree distribution of natural graphs.\\label{followers}"}
d.follow <- histogram.facets(subset(df, initusers == 4096 & mix == 'geom_repost'), 'stat_follower_counts', 'grp')
ggplot(d.follow, aes(x=x, weight=y))+
    stat_ecdf(color=c.blue)+
    xlab('# followers / user (log scale)')+ylab('CDF (log scale)')+
    scale_x_log10(breaks=c(1,10,100,1000))+scale_y_log10(breaks=c(0.1,0.5,1.0))+
    theme_mine
```

```{r reposts, fig.cap="CDF of the number of times a post is reposted, matching traces from real workloads. Due to the power-law graph structure, if users tend to reposts popular recent posts on their timeline, it results in another power-law distribution. Note that that some posts are reposted to over a quarter of the graph (4000 total users).\\label{reposts}"}
d.repost <- histogram.facets(subset(df, initusers == 4096 & mix == 'geom_repost'), 'stat_repost_counts', 'grp')
ggplot(d.repost, aes(x=x, weight=y))+
    stat_ecdf(color=c.blue)+
    xlab('# reposts')+ylab('count')+
    scale_x_log10(breaks=c(1,10,100,1000))+scale_y_log10(breaks=c(0.1,0.2,0.4,0.6,0.8,1.0))+
    xlab('# reposts (log scale)')+ylab('CDF (log scale)')+
    theme_mine
```

>>>>

```{r followers, include=F}
d.follow <- histogram.facets(subset(df, initusers == 4096 & mix == 'geom_repost'), 'stat_follower_counts', 'grp')
ggplot(d.follow, aes(x=x, weight=y))+
    stat_ecdf(color=c.blue)+
    xlab('# followers / user (log scale)')+ylab('CDF (log scale)')+
    scale_x_log10(breaks=c(1,10,100,1000))+scale_y_log10(breaks=c(0.1,0.5,1.0))+
    theme_mine
```
\begin{figure}[t]\centering
\includegraphics{figure/followers-1.pdf}
\caption{CDF of the number of followers for users generated by the
Kronecker synthetic graph generator, matching the power-law degree
distribution of natural graphs.\label{followers}}
\end{figure}

```{r reposts, include=F}
d.repost <- histogram.facets(subset(df, initusers == 4096 & mix == 'geom_repost'), 'stat_repost_counts', 'grp')
ggplot(d.repost, aes(x=x, weight=y))+
    stat_ecdf(color=c.blue)+
    xlab('# reposts')+ylab('count')+
    scale_x_log10(breaks=c(1,10,100,1000))+scale_y_log10(breaks=c(0.1,0.2,0.4,0.6,0.8,1.0))+
    xlab('# reposts (log scale)')+ylab('CDF (log scale)')+
    theme_mine
```
\begin{figure}[t]\centering
\includegraphics{figure/reposts-1.pdf}
\caption{CDF of the number of times a post is reposted, matching traces
from real workloads. Due to the power-law graph structure, if users tend
to reposts popular recent posts on their timeline, it results in another
power-law distribution. Note that that some posts are reposted to over a
quarter of the graph (4000 total users).\label{reposts}}
\end{figure}
